Cool title here

### 2018-02-13 Frontiers_Manuscript/Villasenor-Derbez.Rmd
Added new figure summarizing biological results

Effect sizes for biological indicators are shown in Figure \ref{fig:indicators}. Isla Natividad, the community with the oldest reserve, shows inconsistent effects across indicators and sources of data (*i.e.* fish vs. invertebrates). For example, the reserve had a small effect on fish abundances (Fig \ref{fig:indicators}A), where only year 2010 showed significat effect sizes in fish abundances ($p<0.05$) and all other years oscillated above and under zero ($p > 0.05$). However, in the case of invertebrate abundances (Fig \ref{fig:indicators}B), there was a clear positive effect of the reserve, as all but 1 year (2008) presented positive effect sizes relative to the control site ($p < 0.05$). Maria Elena and Punta Herrero showed no significant increase in fish and invertebrate abundances ($p< 0.05$), except for invertebrates in Punta Herrero for 2014 --right after the implementation of the reserves-- which showed a significant increase (*i.e.* $\lambda_{2014} = 2.5$, $p < 0.05$). Full tables with model coefficients are presented in the supplementary materials (**S1 Table**, **S2 Table**, **S3 Table**).

@@

@@

```{r, fig.width = 3, fig.height = 4, fig.cap = "\\label{fig:lobsters}Time series of lobster catches (A) and revenues (B) in at Isla Natividad (IN; red circles), Maria Elena (ME; blue triangles), and Punta Herrero (PH; green squares)."}

@@

cowplot::plot_grid(plotlist = list(L_catches, L_value),
                   labels = "AUTO",
                   ncol = 1)

>>>>

Effect sizes for biological indicators are shown in Figure \ref{fig:indicators}, and Figure \ref{fig:res_com} shows the summarized biological effects by community. Isla Natividad shows inconsistent effects across data sources (*i.e.* fish vs. invertebrates). For example, the reserve had a small effect on fish abundances (Fig \ref{fig:indicators}A), where only year 2010 showed significat effect sizes in fish abundances ($p<0.05$) and all other years oscillated above and under zero ($p > 0.05$). However, invertebrate abundances (Fig \ref{fig:indicators}B) presented a positive trend relative to the control site before implementation ($p < 0.05$) for all but 1 year (2008). Maria Elena and Punta Herrero showed no significant increase in fish and invertebrate abundances ($p< 0.05$), except for invertebrates in Punta Herrero for 2014 --right after the implementation of the reserves-- which showed a significant increase (*i.e.* $\lambda_{2014} = 2.5$, $p < 0.05$). Full tables with model coefficients are presented in the supplementary materials (**S1 Table**, **S2 Table**, **S3 Table**).

@@

```{r, fig.height = 3, fig.width = 6, fig.cap = "\\label{fig:res_com}Summarized effects of the marne reserves by direction (positive - negative) and significance."}
observe <- function(model){      tidy_terms <- model %>% 
        robust_se() %>%
        filter(grepl(":ZonaReserva", term)) %$%
        str_split(term, pattern = ":", simplify = T) %>% 
        as.tibble() %>% 
        set_colnames(c("Ano", "Zona")) %>% 
        select(-Zona) %>% 
        mutate(Ano = as.numeric(gsub(Ano, pattern = "Ano", replacement = "")))

      p_i <- robust_se(model) %>%
        filter(grepl(":ZonaReserva", term)) %>%
        cbind(tidy_terms) %>%
        mutate(ptest = ((p.value < 0.05)*-1)+0.05)
       return(p_i)}

IN <- list(N_IN, Ni_IN, S_IN, Si_IN, H_IN, Hi_IN, B_IN, L_IN) %>% map_df(.f = observe) %>%
  as.tibble() %>% 
  select(estimate, p.value) %>% 
  mutate(Com = "Isla Natividad",
         n_ind = nrow(.))

ME <- list(N_ME, Ni_ME, S_ME, Si_ME, H_ME, Hi_ME, B_ME, L_ME) %>% map_df(.f = observe) %>%
  as.tibble() %>% 
  select(estimate, p.value) %>% 
  mutate(Com = "Maria Elena",
         n_ind = nrow(.))

PH <- list(N_PH, Ni_PH, S_PH, Si_PH, H_PH, Hi_PH, B_PH, L_PH) %>% map_df(.f = observe) %>%
  as.tibble() %>% 
  select(estimate, p.value) %>% 
  mutate(Com = "Punta Herrero",
         n_ind = nrow(.))

rbind(IN, ME, PH) %>% 
  mutate(direction = case_when(estimate < 0 ~ "Negative",
                               estimate > 0 ~ "Positive"),
         Significance = case_when(p.value < 0.05 ~ "p < 0.05",
                            p.value >= 0.05 ~ "p > 0.05")) %>%
  group_by(Com, direction, Significance, n_ind) %>% 
  summarize(A = n()) %>% 
  ungroup() %>% 
  mutate(A = A/n_ind,
         A = ifelse(direction == "Negative", -A, A),
         Significance = fct_relevel(Significance, "p > 0.05")) %>% 
  ggplot(aes(x = Com, y = A, fill = Significance)) +
  geom_col(color = "black", alpha = 0.8, width = 0.8) +
  geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  coord_flip() +
  labs(x = "Community", y = "Percentage of total coefficients") +
  scale_y_continuous(breaks = c(-0.5, -0.25, 0, 0.25, 0.5, 0.75), limits = c(-0.5, 0.75),
                     labels = scales::percent) +
  theme(legend.text = element_text(size = 8),
        legend.title = element_text(size = 8))
```

@@

```{r, fig.width = 3.5, fig.height = 4, fig.cap = "\\label{fig:lobsters}Time series of lobster catches (A) and revenues (B) in at Isla Natividad (IN; red circles), Maria Elena (ME; blue triangles), and Punta Herrero (PH; green squares)."}

@@

cowplot::plot_grid(plotlist = list(L_catches, L_value),
                   labels = "AUTO",
                   ncol = 1)
```

### 2018-02-13 Frontiers_Manuscript/Villasenor-Derbez.tex
Added new figure summarizing biological results

Effect sizes for biological indicators are shown in Figure
\ref{fig:indicators}. Isla Natividad, the community with the oldest
reserve, shows inconsistent effects across indicators and sources of
data (\emph{i.e.} fish vs.~invertebrates). For example, the reserve had
a small effect on fish abundances (Fig \ref{fig:indicators}A), where
only year 2010 showed significat effect sizes in fish abundances
(\(p<0.05\)) and all other years oscillated above and under zero
(\(p > 0.05\)). However, in the case of invertebrate abundances (Fig
\ref{fig:indicators}B), there was a clear positive effect of the
reserve, as all but 1 year (2008) presented positive effect sizes
relative to the control site (\(p < 0.05\)). Maria Elena and Punta
Herrero showed no significant increase in fish and invertebrate
abundances (\(p< 0.05\)), except for invertebrates in Punta Herrero for
2014 --right after the implementation of the reserves-- which showed a
significant increase (\emph{i.e.} \(\lambda_{2014} = 2.5\),
\(p < 0.05\)). Full tables with model coefficients are presented in the
supplementary materials (\textbf{S1 Table}, \textbf{S2 Table},
\textbf{S3 Table}).

@@

@@

\begin{figure}
\centering
\includegraphics{Villasenor-Derbez_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{\label{fig:unnamed-chunk-5}\label{fig:lobsters}Time series of
lobster catches (A) and revenues (B) in at Isla Natividad (IN; red
circles), Maria Elena (ME; blue triangles), and Punta Herrero (PH; green
squares).}
\end{figure}

>>>>

Effect sizes for biological indicators are shown in Figure
\ref{fig:indicators}, and Figure \ref{fig:res_com} shows the summarized
biological effects by community. Isla Natividad shows inconsistent
effects across data sources (\emph{i.e.} fish vs.~invertebrates). For
example, the reserve had a small effect on fish abundances (Fig
\ref{fig:indicators}A), where only year 2010 showed significat effect
sizes in fish abundances (\(p<0.05\)) and all other years oscillated
above and under zero (\(p > 0.05\)). However, invertebrate abundances
(Fig \ref{fig:indicators}B) presented a positive trend relative to the
control site before implementation (\(p < 0.05\)) for all but 1 year
(2008). Maria Elena and Punta Herrero showed no significant increase in
fish and invertebrate abundances (\(p< 0.05\)), except for invertebrates
in Punta Herrero for 2014 --right after the implementation of the
reserves-- which showed a significant increase (\emph{i.e.}
\(\lambda_{2014} = 2.5\), \(p < 0.05\)). Full tables with model
coefficients are presented in the supplementary materials (\textbf{S1
Table}, \textbf{S2 Table}, \textbf{S3 Table}).

@@

\begin{figure}
\centering
\includegraphics{Villasenor-Derbez_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{\label{fig:unnamed-chunk-5}\label{fig:res_com}Summarized effects of
the marne reserves by direction (positive - negative) and significance.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Villasenor-Derbez_files/figure-latex/unnamed-chunk-6-1.pdf}
\caption{\label{fig:unnamed-chunk-6}\label{fig:lobsters}Time series of
lobster catches (A) and revenues (B) in at Isla Natividad (IN; red
circles), Maria Elena (ME; blue triangles), and Punta Herrero (PH; green
squares).}
\end{figure}
